Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
reviewed 4.3 Solution generalization

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{General architecture of the program synthesizer}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\label{synthesizer-general}
The input specification provided to the program synthesizer is of the form
%$\exists P .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ 
$\exists P .  \forall x.  \sigma(x, P)$ 
where $P$ ranges over functions, $x$ 
 ranges over ground terms and
$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
some finite domain $\mathcal{D}$.
%
The design of our synthesizer consists of two phases, an inductive
synthesis phase and a validation phase, which interact via a finite
set of test vectors {\sc inputs} that is updated incrementally.  Given
the aforementioned specification $\sigma$, the inductive synthesis
procedure tries to find an existential witness $P$ satisfying
the specification $\sigma(x, P)$ for all $x$ in {\sc
  inputs} (as opposed to all $x \in \mathcal{D}$).
%
If the synthesis phase succeeds in finding a witness~$P$, this
witness is a candidate solution to the full synthesis formula.  We
pass this candidate solution to the validation phase, which checks
whether it is a full solution (i.e., $P$ satisfies the
specification $\sigma(x, P)$ for all
$x\in\mathcal{D}$).  If this is the case, then the algorithm
terminates.  Otherwise, additional information is provided to the
inductive synthesis phase in the form of a new counterexample that is
added to the {\sc inputs} set and the loop iterates again.
More details about the general architecture of the synthesiser can
be found in~\cite{DBLP:conf/lpar/DavidKL15}.
%% It is worth noting that each iteration of the loop adds a new input to
%% the finite set $\text{\sc inputs}$ that is used for synthesis.  Given
%% that the full set of inputs $\mathcal{D}$ is finite, this means that
%% the refinement loop can only iterate a finite number of times.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Solution generalisation} 
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
Given the large solution space to be searched during the inductive
synthesis phase, we parametrize the target language, which induces a
lattice of progressively more expressive languages.  This enables us
to start by attempting to synthesize a program at the lowest point on
this lattice and increase the parameters of the language until we
reach a point at which the synthesis succeeds. Whenever we manage to
synthesize a candidate solution at some lower point on the lattice, we
must apply some form of solution generalisation to obtain a full
solution (i.e., a solution in the original search space).

As well as giving us an automatic search procedure, this
parametrisation greatly increases the efficiency of our system since
languages low down the lattice are very easy to decide safety for
(i.e., the validation oracle finds an answer fast). If a program can be
synthesized in a low-complexity language, the whole procedure finishes
much faster than if synthesis had been attempted in a high-complexity
language.

We investigate two different approaches of integrating solution generalisation 
with CEGIS:
\begin{itemize}
\item[1.] The first approach (described in Sec.~\ref{sec:CEGIS-precision-incrementation})
  uses a multi-staged verification phase and performs solution generalisation based on
the plant precision, the number of loop unrollings, 
and the sampling rate. Essentially, it finds a controller for an individual initial state
and input with a bounded time horizon and generalizes to all states,
inputs, and time horizons. The safety check is performed in this approach 
via unfolding of the transition system corresponding to the synthesized controller.

>>>>

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{General architecture of the program synthesizer}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\label{synthesizer-general}
The input specification provided to the program synthesizer is of the form
%$\exists P .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ 
$\exists P .  \forall x.  \sigma(x, P)$ 
where $P$ ranges over functions, $x$ 
 ranges over ground terms and
$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
some finite domain $\mathcal{D}$.
%
The design of our synthesizer consists of two phases, an inductive
synthesis phase and a validation phase, which interact via a finite
set of test vectors {\sc inputs} that is updated incrementally.  Given
the aforementioned specification $\sigma$, the inductive synthesis
procedure tries to find an existential witness $P$ satisfying
the specification $\sigma(x, P)$ for all $x$ in {\sc
  inputs} (as opposed to all $x \in \mathcal{D}$).
%
If the synthesis phase succeeds in finding a witness~$P$, this
witness is a candidate solution to the full synthesis formula.  We
pass this candidate solution to the validation phase, which checks
whether it is a full solution (i.e., $P$ satisfies the
specification $\sigma(x, P)$ for all
$x\in\mathcal{D}$).  If this is the case, then the algorithm
terminates.  Otherwise, additional information is provided to the
inductive synthesis phase in the form of a new counterexample that is
added to the {\sc inputs} set and the loop iterates again.
%
It is worth noting that each iteration of the loop adds a new input to
the finite set $\text{\sc inputs}$ that is used for synthesis.  Given
that the full set of inputs $\mathcal{D}$ is finite, this means that
the refinement loop can only iterate a finite number of times.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Solution generalization} 
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

Given the large solution space to be searched during the inductive
synthesis, we parametrize the target language, which induces a
lattice of progressively more expressive languages.  This enables us
to start by attempting to synthesize a program at the lowest point on
this lattice and increase the parameters of the language until we
reach a point at which the synthesis succeeds. Whenever we manage to
synthesize a solution at some lower point on the lattice, we
must apply some form of solution generalization to obtain a full
solution (i.e., a solution in the original search space).
This parametrization greatly increases the efficiency of our system since
languages low down the lattice are easy to decide safety for
(i.e., the validation oracle finds an answer fast). If a program can be
synthesized in a low-complexity language, the whole procedure finishes
much faster than if synthesis had been attempted in a high-complexity
language. We investigate two different approaches for integrating solution 
generalization into CEGIS:
%
\begin{itemize}
\item[1.] The first approach (described in Sec.~\ref{sec:CEGIS-precision-incrementation})
  uses a multi-staged verification phase and performs solution generalisation based on
the plant precision, the number of loop unrollings, 
and the sampling rate. Essentially, it finds a controller for an individual initial state
and input with a bounded time horizon and generalizes to all states,
inputs, and time horizons. The safety check is performed in this approach 
via unfolding of the transition system corresponding to the synthesized controller.
